Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-28 Submission.Rmd
discussion edits

These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance. The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.

>>>>

These results have implications for practitioners as well, providing support for the idea that managers and supervisors can perhaps predict which characteristics are perceived as supportive to employees’ performance. The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is therefore in some ways encouraging. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.

### 2023-03-28 Submission.tex
discussion edits

These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance. The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. J. A. LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.

>>>>

These results have implications for practitioners as well, providing support for the idea that managers and supervisors can perhaps predict which characteristics are perceived as supportive to employees' performance. The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is therefore in some ways encouraging. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. J. A. LePine et al. (2005) and Podsakoff et al. (2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.
